Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-04-04 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
update chapter 4 intro; update response to R4 minor comments

In studying support recovery problems, restrictions to the thresholding procedures 
are sometimes justified by arguing that such procedures are the ``reasonable'' choice for estimating the support set \citep[e.g.,][]{arias2017distribution}.
We show in this chapter that, perhaps surprisingly, for general error models, thresholding procedures are not always 
optimal, even when the observations are independent.

@@

\begin{remark}[{\bf An open problem\!}\,] As we have seen, the thresholding estimators are no longer optimal 
in the additive model with error-densities heavier than exponential.   Thanks to Theorem 
\ref{thm:likelihood-ratio-thresholding}, the oracle likelihood thresholding procedures are promising alternatives
that can lead us to practical support estimators.

>>>>

In studying support recovery problems, restrictions to the thresholding procedures 
are sometimes justified by arguing that such procedures are the ``reasonable'' choice for estimating the support set \citep[see, e.g.,][]{arias2017distribution}.
We show in this chapter that, perhaps surprisingly, for general error models, thresholding procedures are not always 
optimal, even when the observations are independent.

@@

\begin{remark} As we have seen, the thresholding estimators are no longer optimal 
in the additive model with error-densities heavier than exponential.   Thanks to Theorem 
\ref{thm:likelihood-ratio-thresholding}, the oracle likelihood thresholding procedures are promising alternatives
that can lead us to practical support estimators.

### 2021-04-04 7.GWAS/GWAS.tex
update chapter 4 intro; update response to R4 minor comments

In the previous chapters, we delved deep into the theoretical underpinnings of the phase transition phenomena in high-dimensional multiple testing problems.
The results are interesting in their own right.
However, in the spirit of Feynman, we have not discovered any scientific law, but merely worked out mathematical consequences of our postulated models.
In this chapter, our goal is to relate these predictions to real experimental data from the field of genetics, where large-scale simultaneous hypotheses testing problems often arise.
From such comparisons, we will demonstrate that the phase transition laws are indeed reasonable predictions of some curious phenomena in that field.
The accuracy of our predictions will lend credibility to the application of these ``laws of large dimensions'' in actual applications.

>>>>

In the previous chapters, we delved deep into the theoretical underpinnings of the phase transition phenomena in high-dimensional multiple testing problems.
The results are interesting in their own right.
However, we have not discovered any scientific law in the spirit of Feynman, but merely worked out mathematical consequences of our postulated models.
In this chapter, our goal is to relate these predictions to real experimental data from the field of genetics, where large-scale simultaneous hypotheses testing problems often arise.
From such comparisons, we will demonstrate that the phase transition laws are indeed reasonable predictions of some curious phenomena in that field.
The accuracy of our predictions will lend credibility to the application of these ``laws of large dimensions'' in actual applications.
